### 2021-07-20 article/article.tex
Mention scqubits
Remove linebreak

		The \emph{Spinsim} package is designed so that a single simulator instance can be used to execute many simulations, sweeping through parameters while not needing to be recompiled.
		This is done through the \texttt{sweep\_parameters[]} argument to the user-provided field functions $ \omega_j(t) $.
		% The user can set \texttt{sweep\_parameters[]} to determine parameter for the Hamiltonian.
		First the user must instantiate a \texttt{spinsim.Simulator} object.
		They can then set the value for \texttt{sweep\_parameters[]} for a particular simulation each time \texttt{spinsim.Simulator.evaluate()} is called.
		As \texttt{sweep\_parameters[]} is a \texttt{numpy.ndarray}\cite{harris_array_2020}, one can use this functionality to sweep many parameters using the same simulator object.
		For a use-case example, an MRI experimenter might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
		To do this they could choose to set \texttt{sweep\_parameters = [x, y]},\linebreak and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.
		This feature is demonstrated with examples in the documentation.

@@

	\subsection{Comparison to alternatives}
		We ran the same error and execution time benchmarks on some alternative packages, listed in Table~\ref{tab:external}, to compare \emph{Spinsim}'s performance to theirs.
		\begin{table}[h!]
			\caption{The software packages used for and verification of \emph{Spinsim}.}
			\label{tab:external}
			\begin{tabular}{l|l|p{6.5cm}}
				\textbf{Software package}								&\textbf{Function}					&\textbf{Details}\\
				\hline
				Spinsim													&\texttt{Simulator()}				&The best performing \emph{Spinsim} configuration, using the CF4 integrator and the rotating frame mode. This was run both on CPU and GPU.
				\\
				\hline
				QuTip\cite{johansson_qutip_2013}						&\texttt{sesolve()}					&The Schr\"odinger equation solver from the popular \emph{python} quantum mechanics library, \emph{QuTip}.
				This was chosen as a comparison to a specially designed solver used within the physics community for this application.
				Like \emph{Spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelisation.\\
				\hline
				Mathematica\cite{wolfram_research_inc_mathematica_2020}	&\texttt{NDSolve()}					&A generic ODE solver from the \emph{Mathematica} software.
				This was chosen as it is popular with our lab group for simulating magnetometry experiments.\\
				\hline
				SciPy\cite{virtanen_scipy_2020}							&\texttt{integrate.ivp\_solve()}	&A generic ODE solver from the popular \emph{python} scientific computing library.
				This was chosen as a comparison to a generic solver from within the python ecosystem.
			\end{tabular}
		\end{table}
		To obtain simulation results of different accuracies, the step sizes of the alternative integrators were limited to a maximum value.
		In some cases, the maximum number of steps was modified in some cases to allow for the smaller step sizes.
		% In each case, the step sizes of the alternative integrators were limited to a maximum value 
		Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.

>>>>

		The \emph{Spinsim} package is designed so that a single simulator instance can be used to execute many simulations, sweeping through parameters while not needing to be recompiled.
		This is done through the \texttt{sweep\_parameters[]} argument to the user-provided field functions $ \omega_j(t) $.
		% The user can set \texttt{sweep\_parameters[]} to determine parameter for the Hamiltonian.
		First the user must instantiate a \texttt{spinsim.Simulator} object.
		They can then set the value for \texttt{sweep\_parameters[]} for a particular simulation each time \texttt{spinsim.Simulator.evaluate()} is called.
		As \texttt{sweep\_parameters[]} is a \texttt{numpy.ndarray}\cite{harris_array_2020}, one can use this functionality to sweep many parameters using the same simulator object.
		For a use-case example, an MRI experimenter might want to simulate many spin systems at different locations $ (x, y) $, in a magnetic field gradient $ \omega_z(t) = x - 2 y $.
		To do this they could choose to set \texttt{sweep\_parameters = [x, y]}, and define \texttt{field\_sample[2] = sweep\_parameters[0] - 2*sweep\_parameters[1]}.% \linebreak
		This feature is demonstrated with examples in the documentation.

@@

	\subsection{Comparison to alternatives}
		We ran the same error and execution time benchmarks on some alternative packages, listed in Table~\ref{tab:external}, to compare \emph{Spinsim}'s performance to theirs.
		\begin{table}[h!]
			\caption{The software packages used for and verification of \emph{Spinsim}.}
			\label{tab:external}
			\begin{tabular}{l|l|p{6.5cm}}
				\textbf{Software package}								&\textbf{Function}					&\textbf{Details}\\
				\hline
				Spinsim													&\texttt{Simulator()}				&The best performing \emph{Spinsim} configuration, using the CF4 integrator and the rotating frame mode. This was run both on CPU and GPU.
				\\
				\hline
				QuTip\cite{johansson_qutip_2013}						&\texttt{sesolve()}					&The Schr\"odinger equation solver from the popular \emph{python} quantum mechanics library, \emph{QuTip}.
				This was chosen as a comparison to a specially designed solver used within the physics community for this application.
				Some quantum mechanics simulation packages such as the recent \emph{scqubits}~\cite{groszkowski_scqubits_2021} use \emph{QuTip} for calculating time evolution.
				Like \emph{Spinsim}, \emph{QuTip} allows users to sample from compiled functions, and uses parallelisation.\\
				\hline
				Mathematica\cite{wolfram_research_inc_mathematica_2020}	&\texttt{NDSolve()}					&A generic ODE solver from the \emph{Mathematica} software.
				This was chosen as it is popular with our lab group for simulating magnetometry experiments.\\
				\hline
				SciPy\cite{virtanen_scipy_2020}							&\texttt{integrate.ivp\_solve()}	&A generic ODE solver from the popular \emph{python} scientific computing library.
				This was chosen as a comparison to a generic solver from within the python ecosystem.
			\end{tabular}
		\end{table}
		To obtain simulation results of different accuracies, the step sizes of the alternative integrators were limited to a maximum value.
		In some cases, the maximum number of steps was modified in some cases to allow for the smaller step sizes.
		% In each case, the step sizes of the alternative integrators were limited to a maximum value 
		Apart from that, the integrator settings were left untouched from the default values, as a representation of what a user would experience using a generic solver for spin system problems.
